---
title: "Problem Set 8"
author: "Bhavik Kollipara"
date: "10/28/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Question 1

n = 963
mu = 121.1
sample sd= 17.6

a)CI = 80%
 1-alpha =0.8
 alpha = 0.2
 1 - alpha/2 = 0.9

```{r}
n<- 963
mu<- 121.1
ssd<- 17.6
se<- ssd/sqrt(n)
q<-qnorm(0.9)
#upper limit
mu + q*se
#lower limit
mu - q*se
```
b)CI= 95%
 1-alpha =0.95
 alpha = 0.1
 1 - alpha/2 = 0.975

```{r}
q<-qnorm(0.975)
#upper limit
mu + q*se
#lower limit
mu - q*se
```

c)CI= 99%
 1-alpha =0.99
 alpha = 0.01
 1 - alpha/2 = 0.995

```{r}
q<-qnorm(0.995)
#upper limit
mu + q*se
#lower limit
mu - q*se
```

### Question 2


Xbar = 0.58
n = 1009

a)
CI= 95%
 1-alpha =0.95
 alpha = 0.05
 1 - alpha/2 = 0.975

```{r}
n<- 1009
xbar<- 0.58
sd<- sqrt(xbar*(1-xbar)/n)
q<-qnorm(.975)
#upper limit
xbar + q*sd
#lower limit
xbar - q*sd
```
b) 

2* qnorm(0.975) * (xbar*(1-xbar)/n)^(1/2)= 0.02
=2* 1.96 * ((0.58*0.42/n)^(1/2)) = 0.02
=(0.2436/n)^(1/2) = 0.0051
n=9358

### Question 3
a)
237/720 questions are right.
P(question correct) = 0.25
e(x)= 720 * 0.25 = 180

b)  1 - pbinom(236, 720, 0.25)

c)
“The significance probability is **small**. This means a number of correct answers this high would be **surprising** if the students were just randomly guessing. The data is thus **highly incompatible** with the null hypothesis. We have **strong evidence** in favor of the alternative hypothesis that students are doing better than random guessing."


### Question 4
a) Given
H0 : p = 1/6 vs H1 : p < 1/6.
getting 15 sixes in 100 rolls.

p=
```{r}
pbinom(15,100,1/6)
```


b)
H0 : p = 32/663 vs H1 : p < 32/663. 

p=
```{r}
pbinom(59,1000,32/663)
```

c)
H0 : p = 0.5
two-tailed test

p=
```{r}
#left test
pbinom(1150,2215,0.5)
#right test
1 - pbinom(1149,2215,0.5)
#two tailed test (2 times of smaller p-values of right and left tests)
2*(1 - pbinom(1149,2215,0.5))
```
p=0.07 is NOT statistically significant. Therefore, we cannot reject the null hypothesis.

d)
H0 : p = 0.25
H1 : p > 0.25

p=
```{r}
1 - pbinom(236,720,0.25)
```
as p is statistically significant, we can reject the null hypothesis. 

### Question 5
```{r}
ANESpilot <- read.table("ANESpilot.txt", header = TRUE)
```
a) 
H0 : p = 0.5
H1 : p != 0.5(p not equal to 0.5)

b)n = 1163 and p =0.5

c)
Clinton higher than Trump=
```{r}
sum(ANESpilot$ClintonFT > ANESpilot$TrumpFT)
```

Trump higher than Clinton=
```{r}
sum(ANESpilot$ClintonFT < ANESpilot$TrumpFT)
```

d)

```{r}
#left test
pbinom(623,1163,0.5)
#right test
1 - pbinom(622,1163,0.5)
#two tailed test (2 times of smaller p-values of right and left tests)
2*(1 - pbinom(622,1163,0.5))
```

e) as p=0.016 which is statistically significant. That is we can reject the null hypothesis. 


CI=
```{r}
R <- ANESpilot$ClintonFT
S <- ANESpilot$TrumpFT
Q <- R - S
n <- 1163
mu<- mean(Q)
std <- sd(Q)
se <- std/sqrt(n)
q<- qnorm(0.975)
mu
mu - q*se
mu + q*se
```
Based on this, we can say that direction of bias is towards Clinton.
