---
title: "Problem Set 7"
author: "Bhavik Kollipara"
date: "10/20/2021"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### QUESTION 1

a) 5/59

b) False

c) False

d) False

e) False

### QUESTION 2

a) E[X] = mu = 0.3* -2 + 0.6 * -1 + 0.1*12
= 0

b) Var[X]
E[X^2]-(E[X])^2= 16.2

c) E(X)= Population mean = mu = 0

d) n = 100
variance=16.2/100 = 0.162

e) P(sample mean>0.5) = 1 - P(sample mean $/le$ 0.5)
```{r}
1 - pnorm(0.5,mean = 0,sd = sqrt(0.162))
```
## QUESTION 3

standard deviation = 30mins
n=20
sum of means(in hours) = 100
sd= standard deviation * (n)^(1/2)

Probability (at least 105 hours)

```{r}
1 - pnorm(104.99999,100, 0.5*sqrt(20))
```
## QUESTION 4

let X be daily fluctations in value stock
let Y be daily fluctations in growth stock
Given expectation and variance for each day for value stock and growth stock
E[X_i] = 0.01
Var[X_i] = 0.01

E[X_i] = 0
Var[X_i] = 0.25

n= 400
=> 
E[X] = 50 + E[X_1] + E[X_2]+ ..... E[X_400] = 50 + 400 * 0.01 = 54
Var[X] = Var[X_1] + Var[X_2] + ...... Var[X_400] = 400 * 0.01 = 4
=>sd[X] = 2
E[Y] = 50 + E[Y_1] + E[Y_2]+ ..... E[Y_400] = 50 + 400 * 0 = 50
Var[Y] = Var[Y_1] + Var[Y_2] + ...... Var[Y_400] = 400 * 0.25 = 100
=> sd[Y] = 10 

a) P(X>50) = 1 - P(X $\le$ 50)

```{r}
1 - pnorm(50,54,2)
```
b) P(Y>50) = 1 - P(Y $\le$ 50)

```{r}
1 - pnorm(50,50,10)
```
c) P(X $\ge$ 70) = 1 - P(X $\le$ 70)

```{r}
1 - pnorm(70,54,2)
```
d) P(Y $\ge$ 70) = 1 - P(Y $\le$ 70)
```{r}
1 - pnorm(70,50,10)
```
e) lets take Z = Y-X as new Random variable
E[Z] = E[Y] + E[X] = 0 - 4 = -4
Var[Z] = Var[Y] + Var[X] = 100 + 4 = 104

P=
```{r}
1 - pnorm(0,-4,sqrt(104))
```




## QUESTION 5

a) P(40 $\le$ X $\le$ 60) is given by

```{r}
pbinom(60,100,0.5) - pbinom(39,100,0.5)
```
b) 
E(X)= population mean = p = 0.5
Standard deviation of sample mean = (p(1-p)/n)^(1/2)
P(0.395 $\le$ X $\le$ 0.605) is given by

```{r}
pnorm(0.605,0.5,0.05) - pnorm(0.395,0.5,0.05)
```



## QUESTION 6
``` {r}
household_sizes <- rep(1:7, c(27, 34, 16, 13, 6, 3, 1))
```
a) sample_mean=
```{r}
sample_mean<- mean(household_sizes)
sample_mean
```
b)
```{r}
sd= sd(household_sizes)
sd
```
c) 
```{r}
esti_sd_err = sd(household_sizes)/sqrt(100)
esti_sd_err
```

d)Approximate probability that the absolute value of the error in a survey of this form and size is less than 0.5 given by
```{r}
pnorm(0.5,mean = 0, sd = esti_sd_err) - pnorm(-0.5,mean = 0, sd = esti_sd_err)
```
e) P(etween 2 and 3)
```{r}
pnorm(3,mean = 2.5, sd = esti_sd_err) - pnorm(2,mean = 2.5, sd = esti_sd_err)
```
as probability is approximately equal to 0.9997, we can say that average household size for all U.S. households is between 2 and 3
