---
title: "Pulse Rates of Peruvian Indians"
author: "Bhavik Kollipara"
date: "10/13/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The data
https://mtrosset.pages.iu.edu/ StatInfeR/Data/pulses.dat

The data set can be scanned in from the web:

```{r}
pulses.rate <- scan("https://mtrosset.pages.iu.edu/StatInfeR/Data/pulses.dat")
```


```{r}
library(ggplot2)

```


```{r}
pulses.df <- data.frame(Rate =pulses.rate)
```

a) Graph the e-cdf
```{r}
ggplot(pulses.df, aes(Rate)) + stat_ecdf(geom = "step") + ylab("Ecdf")
```

b) plug-in estimates of population mean and variance
```{r}
len= length(pulses.df$Rate)
# Plug-in 
sum(pulses.df$Rate)/len
```
```{r}
#plugin
v=sqrt(mean(pulses.df$Rate^2) - mean(pulses.df$Rate)^2)
v
```

```{r}
#sample
mean(pulses.df$Rate)
sd(pulses.df$Rate)
```
c) plug-in estimates of median and IQR
```{r}
#plugin median
r_sort <- sort(pulses.df$Rate)
r_sort[as.integer(len/2)]

#plugin IQR
r_25q<- r_sort[as.integer(len/4)]
r_75q<- r_sort[as.integer(3*len/4)]

IQR <-r_75q - r_25q
IQR

```

d) Ratio of plug-in estimate of IQR to sqrt of plug in estimate of variance
```{r}
IQR/sqrt(v)
```

e) Box Plot
```{r}
ggplot(pulses.df, aes(y=Rate)) + geom_boxplot()
```

f) Normal probability plot
```{r}
qqnorm(pulses.df$Rate)
```

g) Kernel Density Plot
```{r}
ggplot(pulses.df, aes(x= Rate)) +geom_density()
```

h)Normal Distribution (Yes or Not ?)
```{r}

ggplot(pulses.df, aes(sample = Rate)) + stat_qq()
```
Looks like the distribution doesn't follow Normal Distribution as the data in the sample doesn't have a straight trend across the origin.

